Software Citation Principles

### 2016-06-23 sc-principles/software-citation-principles.tex
remove second paragraph of 5.1 - closes #151

Again, the specific decision of what is appropriate to cite must be made by the author(s) of the product.
However, an illustrative example is the use of Microsoft Excel in research.
We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.  Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), research presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.
This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g. Word, Excel) or programming languages.  Provide references only for specialized software.''~\cite{powl-citing-software}  In other words, if using different software could produce different data or results, then the software used should be cited.

>>>>

%Again, the specific decision of what is appropriate to cite must be made by the author(s) of the product.
%However, an illustrative example is the use of Microsoft Excel in research.
%We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.  Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), research presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.
%This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g. Word, Excel) or programming languages.  Provide references only for specialized software.''~\cite{powl-citing-software}  In other words, if using different software could produce different data or results, then the software used should be cited.
